Example of Market Simulator Dasbhaord

### 2021-09-03 dashboard_example.Rmd

  # Segment 1 market shares
  per1_share_denom <- sum(per1_prod1_exp, per1_prod2_exp, per1_prod3_exp, per1_prod4_exp)
  per1_prod1_share <- 100 * (per1_prod1_exp / per1_share_denom)
  per1_prod2_share <- 100 * (per1_prod2_exp / per1_share_denom)
  per1_prod3_share <- 100 * (per1_prod3_exp / per1_share_denom)
  per1_prod4_share <- 100 * (per1_prod4_exp / per1_share_denom)

  # Segment 2 predicted betas
  per2_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,3])

  # Segment 2 expected utilities
  per2_prod1_exp <- exp(t(prod_choice[,2]) %*% as.matrix(per2_betas))
  per2_prod2_exp <- exp(t(prod_choice[,3]) %*% as.matrix(per2_betas))
  per2_prod3_exp <- exp(t(prod_choice[,4]) %*% as.matrix(per2_betas))
  per2_prod4_exp <- exp(t(prod_choice[,5]) %*% as.matrix(per2_betas))

  # Segment 2 market shares
  per2_share_denom <- sum(per2_prod1_exp, per2_prod2_exp, per2_prod3_exp, per2_prod4_exp)
  per2_prod1_share <- 100 * (per2_prod1_exp / per2_share_denom)
  per2_prod2_share <- 100 * (per2_prod2_exp / per2_share_denom)
  per2_prod3_share <- 100 * (per2_prod3_exp / per2_share_denom)
  per2_prod4_share <- 100 * (per2_prod4_exp / per2_share_denom)

  # Segment 3 predicted betas
  per3_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,4])

  # Segment 3 expected utilities
  per3_prod1_exp <- exp(t(prod_choice[,2]) %*% as.matrix(per3_betas))
  per3_prod2_exp <- exp(t(prod_choice[,3]) %*% as.matrix(per3_betas))
  per3_prod3_exp <- exp(t(prod_choice[,4]) %*% as.matrix(per3_betas))
  per3_prod4_exp <- exp(t(prod_choice[,5]) %*% as.matrix(per3_betas))

  # Segment 3 market shares
  per3_share_denom <- sum(per3_prod1_exp, per3_prod2_exp, per3_prod3_exp, per3_prod4_exp)
  per3_prod1_share <- 100 * (per3_prod1_exp / per3_share_denom)
  per3_prod2_share <- 100 * (per3_prod2_exp / per3_share_denom)
  per3_prod3_share <- 100 * (per3_prod3_exp / per3_share_denom)
  per3_prod4_share <- 100 * (per3_prod4_exp / per3_share_denom)

  # Data for plotly
  plot_data <- data.frame(
    Value = c(
      # Segment 1
      per1_prod1_share, per1_prod2_share, per1_prod3_share, per1_prod4_share, 
      # Segment 2
      per2_prod1_share, per2_prod2_share, per2_prod3_share, per2_prod4_share,
      # Segment 3
      per3_prod1_share, per3_prod2_share, per3_prod3_share, per3_prod4_share
    ),
    Product = c(input$prod1_name, input$prod2_name, input$prod3_name, input$prod4_name),
    Persona = c(
      rep(input$per1_name, 4), 
      rep(input$per2_name, 4), 
      rep(input$per3_name, 4)
    )
  )

  ggplotly(
    plot_data %>% 
      # Factor Product and Segment with ordered=TRUE
      mutate(
        Product = factor(
          Product, 
          levels = c(input$prod1_name, input$prod2_name, input$prod3_name, input$prod4_name), 
          ordered = TRUE
        ),
        Persona = factor(
          Persona, 
          levels = c(input$per1_name, input$per2_name, input$per3_name), 
          ordered = TRUE
        )
      ) %>% 
      ggplot(aes(y = Value, x = Product, fill = Persona)) +
      geom_bar(position = "dodge", stat = "identity") +
      labs(x="", y = "Market Share") + 
      scale_fill_manual(values = c("#FFC30B", "#28a153", "#c23838")) +
      theme(
        legend.position = "right",
        panel.background = element_blank(),
        panel.grid.major.y = element_line(color = "#D3D3D3")
      )
    )
})

# Compute and render the market share as a table
renderTable({
  prod_choice = prod_reactive()
  per_choice = per_reactive()

  # Segment 1 predicted betas
  per1_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,2])

  # Segment 1 expected utilities
  per1_prod1_exp <- exp(t(prod_choice[,2]) %*% as.matrix(per1_betas))
  per1_prod2_exp <- exp(t(prod_choice[,3]) %*% as.matrix(per1_betas))
  per1_prod3_exp <- exp(t(prod_choice[,4]) %*% as.matrix(per1_betas))
  per1_prod4_exp <- exp(t(prod_choice[,5]) %*% as.matrix(per1_betas))

  # Segment 1 market shares
  per1_share_denom <- sum(per1_prod1_exp, per1_prod2_exp, per1_prod3_exp, per1_prod4_exp)
  per1_prod1_share <- 100 * (per1_prod1_exp / per1_share_denom)
  per1_prod2_share <- 100 * (per1_prod2_exp / per1_share_denom)
  per1_prod3_share <- 100 * (per1_prod3_exp / per1_share_denom)
  per1_prod4_share <- 100 * (per1_prod4_exp / per1_share_denom)

  # Segment 2 predicted betas
  per2_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,3])

  # Segment 2 expected utilities
  per2_prod1_exp <- exp(t(prod_choice[,2]) %*% as.matrix(per2_betas))
  per2_prod2_exp <- exp(t(prod_choice[,3]) %*% as.matrix(per2_betas))
  per2_prod3_exp <- exp(t(prod_choice[,4]) %*% as.matrix(per2_betas))
  per2_prod4_exp <- exp(t(prod_choice[,5]) %*% as.matrix(per2_betas))

  #  Segment 2 market shares
  per2_share_denom <- sum(per2_prod1_exp, per2_prod2_exp, per2_prod3_exp, per2_prod4_exp)
  per2_prod1_share <- 100 * (per2_prod1_exp / per2_share_denom)
  per2_prod2_share <- 100 * (per2_prod2_exp / per2_share_denom)
  per2_prod3_share <- 100 * (per2_prod3_exp / per2_share_denom)
  per2_prod4_share <- 100 * (per2_prod4_exp / per2_share_denom)

  # Segment 3 predicted betas
  per3_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,4])

  # Segment 3 expected utilities
  per3_prod1_exp <- exp(t(prod_choice[,2]) %*% as.matrix(per3_betas))
  per3_prod2_exp <- exp(t(prod_choice[,3]) %*% as.matrix(per3_betas))
  per3_prod3_exp <- exp(t(prod_choice[,4]) %*% as.matrix(per3_betas))
  per3_prod4_exp <- exp(t(prod_choice[,5]) %*% as.matrix(per3_betas))

  # Segment 3 market shares
  per3_share_denom <- sum(per3_prod1_exp, per3_prod2_exp, per3_prod3_exp, per3_prod4_exp)
  per3_prod1_share <- 100 * (per3_prod1_exp / per3_share_denom)
  per3_prod2_share <- 100 * (per3_prod2_exp / per3_share_denom)
  per3_prod3_share <- 100 * (per3_prod3_exp / per3_share_denom)
  per3_prod4_share <- 100 * (per3_prod4_exp / per3_share_denom)

  # Table
  data <- data.frame(
    Shares = c(
      # Segment 1
      per1_prod1_share, per1_prod2_share, per1_prod3_share, per1_prod4_share, 
      # Segment 2
      per2_prod1_share, per2_prod2_share, per2_prod3_share, per2_prod4_share,
      # Segment 3
      per3_prod1_share, per3_prod2_share, per3_prod3_share, per3_prod4_share
    ),
    Product = c(input$prod1_name, input$prod2_name, input$prod3_name, input$prod4_name),
    Persona = c(
      rep(input$per1_name, 4), 
      rep(input$per2_name, 4), 
      rep(input$per3_name, 4)
    )
  ) %>% 
    pivot_wider(names_from = Persona, values_from = Shares)

>>>>

  # Segment 1 market shares
  seg1_share_denom <- sum(seg1_prod1_exp, seg1_prod2_exp, seg1_prod3_exp, seg1_prod4_exp)
  seg1_prod1_share <- 100 * (seg1_prod1_exp / seg1_share_denom)
  seg1_prod2_share <- 100 * (seg1_prod2_exp / seg1_share_denom)
  seg1_prod3_share <- 100 * (seg1_prod3_exp / seg1_share_denom)
  seg1_prod4_share <- 100 * (seg1_prod4_exp / seg1_share_denom)

  # Segment 2 predicted betas
  seg2_betas <- as.matrix(gammas) %*% as.matrix(seg_choice[,3])

  # Segment 2 expected utilities
  seg2_prod1_exp <- exp(t(prod_choice[,2]) %*% as.matrix(seg2_betas))
  seg2_prod2_exp <- exp(t(prod_choice[,3]) %*% as.matrix(seg2_betas))
  seg2_prod3_exp <- exp(t(prod_choice[,4]) %*% as.matrix(seg2_betas))
  seg2_prod4_exp <- exp(t(prod_choice[,5]) %*% as.matrix(seg2_betas))

  # Segment 2 market shares
  seg2_share_denom <- sum(seg2_prod1_exp, seg2_prod2_exp, seg2_prod3_exp, seg2_prod4_exp)
  seg2_prod1_share <- 100 * (seg2_prod1_exp / seg2_share_denom)
  seg2_prod2_share <- 100 * (seg2_prod2_exp / seg2_share_denom)
  seg2_prod3_share <- 100 * (seg2_prod3_exp / seg2_share_denom)
  seg2_prod4_share <- 100 * (seg2_prod4_exp / seg2_share_denom)

  # Segment 3 predicted betas
  seg3_betas <- as.matrix(gammas) %*% as.matrix(seg_choice[,4])

  # Segment 3 expected utilities
  seg3_prod1_exp <- exp(t(prod_choice[,2]) %*% as.matrix(seg3_betas))
  seg3_prod2_exp <- exp(t(prod_choice[,3]) %*% as.matrix(seg3_betas))
  seg3_prod3_exp <- exp(t(prod_choice[,4]) %*% as.matrix(seg3_betas))
  seg3_prod4_exp <- exp(t(prod_choice[,5]) %*% as.matrix(seg3_betas))

  # Segment 3 market shares
  seg3_share_denom <- sum(seg3_prod1_exp, seg3_prod2_exp, seg3_prod3_exp, seg3_prod4_exp)
  seg3_prod1_share <- 100 * (seg3_prod1_exp / seg3_share_denom)
  seg3_prod2_share <- 100 * (seg3_prod2_exp / seg3_share_denom)
  seg3_prod3_share <- 100 * (seg3_prod3_exp / seg3_share_denom)
  seg3_prod4_share <- 100 * (seg3_prod4_exp / seg3_share_denom)

  # Data for plotly
  plot_data <- data.frame(
    Value = c(
      # Segment 1
      seg1_prod1_share, seg1_prod2_share, seg1_prod3_share, seg1_prod4_share, 
      # Segment 2
      seg2_prod1_share, seg2_prod2_share, seg2_prod3_share, seg2_prod4_share,
      # Segment 3
      seg3_prod1_share, seg3_prod2_share, seg3_prod3_share, seg3_prod4_share
    ),
    Product = c(input$prod1_name, input$prod2_name, input$prod3_name, input$prod4_name),
    Segment = c(
      rep(input$per1_name, 4), 
      rep(input$per2_name, 4), 
      rep(input$per3_name, 4)
    )
  )

  ggplotly(
    plot_data %>% 
      # Factor Product and Segment with ordered=TRUE
      mutate(
        Product = factor(
          Product, 
          levels = c(input$prod1_name, input$prod2_name, input$prod3_name, input$prod4_name), 
          ordered = TRUE
        ),
        Segment = factor(
          Segment, 
          levels = c(input$per1_name, input$per2_name, input$per3_name), 
          ordered = TRUE
        )
      ) %>% 
      ggplot(aes(y = Value, x = Product, fill = Segment)) +
      geom_bar(position = "dodge", stat = "identity") +
      labs(x="", y = "Market Share") + 
      scale_fill_manual(values = c("#FFC30B", "#28a153", "#c23838")) +
      theme(
        legend.position = "right",
        panel.background = element_blank(),
        panel.grid.major.y = element_line(color = "#D3D3D3")
      )
    )
})

# Compute and render the market share as a table
renderTable({
   prod_choice = prod_reactive()
   seg_choice = seg_reactive()

  # Segment 1 market shares
  seg1_share_denom <- sum(seg1_prod1_exp, seg1_prod2_exp, seg1_prod3_exp, seg1_prod4_exp)
  seg1_prod1_share <- 100 * (seg1_prod1_exp / seg1_share_denom)
  seg1_prod2_share <- 100 * (seg1_prod2_exp / seg1_share_denom)
  seg1_prod3_share <- 100 * (seg1_prod3_exp / seg1_share_denom)
  seg1_prod4_share <- 100 * (seg1_prod4_exp / seg1_share_denom)

  # Segment 2 predicted betas
  seg2_betas <- as.matrix(gammas) %*% as.matrix(seg_choice[,3])

  # Segment 2 expected utilities
  seg2_prod1_exp <- exp(t(prod_choice[,2]) %*% as.matrix(seg2_betas))
  seg2_prod2_exp <- exp(t(prod_choice[,3]) %*% as.matrix(seg2_betas))
  seg2_prod3_exp <- exp(t(prod_choice[,4]) %*% as.matrix(seg2_betas))
  seg2_prod4_exp <- exp(t(prod_choice[,5]) %*% as.matrix(seg2_betas))

  # Segment 2 market shares
  seg2_share_denom <- sum(seg2_prod1_exp, seg2_prod2_exp, seg2_prod3_exp, seg2_prod4_exp)
  seg2_prod1_share <- 100 * (seg2_prod1_exp / seg2_share_denom)
  seg2_prod2_share <- 100 * (seg2_prod2_exp / seg2_share_denom)
  seg2_prod3_share <- 100 * (seg2_prod3_exp / seg2_share_denom)
  seg2_prod4_share <- 100 * (seg2_prod4_exp / seg2_share_denom)

  # Segment 3 predicted betas
  seg3_betas <- as.matrix(gammas) %*% as.matrix(seg_choice[,4])

  # Segment 3 expected utilities
  seg3_prod1_exp <- exp(t(prod_choice[,2]) %*% as.matrix(seg3_betas))
  seg3_prod2_exp <- exp(t(prod_choice[,3]) %*% as.matrix(seg3_betas))
  seg3_prod3_exp <- exp(t(prod_choice[,4]) %*% as.matrix(seg3_betas))
  seg3_prod4_exp <- exp(t(prod_choice[,5]) %*% as.matrix(seg3_betas))

  # Segment 3 market shares
  seg3_share_denom <- sum(seg3_prod1_exp, seg3_prod2_exp, seg3_prod3_exp, seg3_prod4_exp)
  seg3_prod1_share <- 100 * (seg3_prod1_exp / seg3_share_denom)
  seg3_prod2_share <- 100 * (seg3_prod2_exp / seg3_share_denom)
  seg3_prod3_share <- 100 * (seg3_prod3_exp / seg3_share_denom)
  seg3_prod4_share <- 100 * (seg3_prod4_exp / seg3_share_denom)

  # Table
  data <- data.frame(
    Shares = c(
      # Segment 1
      seg1_prod1_share, seg1_prod2_share, seg1_prod3_share, seg1_prod4_share, 
      # Segment 2
      seg2_prod1_share, seg2_prod2_share, seg2_prod3_share, seg2_prod4_share,
      # Segment 3
      seg3_prod1_share, seg3_prod2_share, seg3_prod3_share, seg3_prod4_share
    ),
    Product = c(input$prod1_name, input$prod2_name, input$prod3_name, input$prod4_name),
    Segment = c(
      rep(input$per1_name, 4), 
      rep(input$per2_name, 4), 
      rep(input$per3_name, 4)
    )
  ) %>% 
    pivot_wider(names_from = Segment, values_from = Shares)
